---
title: "Stock Analysis Of Intuitive Surgical, Inc"
author: "Steffen Zou Weilun"
date: "10 November 2020"
output:
  pdf_document: default
  html_document: default
---

Intuitive Surgical, Inc is the pioneer and a global technology leader in robotic-assisted, minimally invasive surgery.

Its main product is the da Vinci Surgical System, which is a platform for robotic-assisted surgery, designed to enable complex surgery using a minimally invasive approach. Compared to traditional open procedures that require large incisions, robotic surgery uses a few small incisions.

I will explore the company's financial data to find out the following:

1. Does it have recurring revenue?
2. Is there growing demand for its products / services?
3. Can the company operate without relying on external funding?

```{r message=FALSE, echo=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(lubridate)

financial <- read_excel('ISRG.xlsx', sheet = 'overall')
recurringRevenue <- read_excel('ISRG.xlsx', sheet = 'recurring revenue')

names(financial) <- gsub('[ -]', '_', names(financial))
names(recurringRevenue) <- gsub(' ', '_', names(recurringRevenue))

# Calculate year-over-year gross profit growth
yoy_gross_profit_growth <- with(financial
                                , gross_profit[-nrow(financial)] / 
                                             gross_profit[-1] - 1)
yoy_gross_profit_growth <- c(yoy_gross_profit_growth, NA)
financial$yoy_gross_profit_growth <- yoy_gross_profit_growth

# Calculate recurring revenue as proportion of total revenue
financial$proportion_recurring <- with(financial
                                       , recurring_revenue / total_revenue)

# Calculate recurring revenue segment as proportion of total recurring revenue
totalRecurring <- select(financial, fiscal_year_ended
                         , total_recurring_revenue = recurring_revenue)
recurringRevenue <- 
  inner_join(recurringRevenue, totalRecurring
                               , by = 'fiscal_year_ended') %>%
  mutate(proportion = recurring_revenue / total_recurring_revenue)

# Calculate year-over-year recurring revenue growth for each segment
recurr_current <- 
  recurringRevenue$recurring_revenue[1:(nrow(recurringRevenue)-3)]
recurr_prev <- 
  recurringRevenue$recurring_revenue[-(1:3)]
yoy_recurr_growth <- c(recurr_current / recurr_prev - 1, NA, NA, NA)

recurringRevenue$yoy_growth <- yoy_recurr_growth

# Calculate whether meet growth KPI
growth_kpi <- 0.1

recurringRevenue <- 
  mutate(recurringRevenue
         , met_growth_KPI = case_when(
             yoy_growth >= growth_kpi ~ 'Yes'
           , yoy_growth < growth_kpi ~ 'No'
         ))

# Calculate free cash flow and free cash flow margin
financial <- 
    mutate(financial
           , free_cash_flow = operating_cash_flow - capital_expenditure
           , fcf_margin = free_cash_flow / total_revenue)
```


## 1. Does It Have Recurring Revenue?

```{r fig.width=5, echo=FALSE}
recurring <-
    head(financial, n = 3) %>%
    select(fiscal_year_ended, proportion_recurring)

ylim_max <- max(recurring$proportion_recurring) * 1.04
title <- 'Recurring revenue as proportion of total revenue 
(2017 to 2019)'
    
ggplot(data = recurring
       , aes(x = format(fiscal_year_ended, '%Y-%b')
             , y = proportion_recurring)) +
    geom_col(fill = '#99ccff') +
    labs(x = 'Fiscal year ended', y = 'Proportion of total revenue') +
    ggtitle(title) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)
          , panel.grid = element_blank()
          , axis.text.y = element_blank()) +
    coord_cartesian(ylim = c(0, ylim_max)) +
    geom_text(aes(label = paste(round(proportion_recurring * 100, 1)
                                , '%', sep = ''))
              , vjust = -0.7, size = 3.1)
```

From this bar plot, it shows that the company has recurring revenue which is about 72% of total revenue.

```{r echo=FALSE}
recurringProportion <- 
  recurringRevenue %>% 
  filter(fiscal_year_ended >= ymd(20170101))

ylim_max <- max(recurringProportion$proportion) * 1.05
  
ggplot(data = recurringProportion
       , aes(x = segment, y = proportion, fill = segment)) +
  geom_col() +
  facet_grid(cols = vars(format(fiscal_year_ended, '%Y'))) +
  geom_text(aes(label = paste(round(proportion * 100, 1), '%', sep = ''))
            , vjust = -0.6, size = 3) +
  labs(x = '', y = 'Proportion of recurring revenue') +
  ggtitle('Segment as proportion of recurring revenue') +
  theme(axis.text = element_blank()
        , axis.ticks = element_blank()
        , plot.title = element_text(hjust = 0.5)
        , panel.grid = element_blank()) +
  coord_cartesian(ylim = c(0, ylim_max))
```

Its recurring revenue comes from instruments and accessories, services, and operating lease. 74.3% of its recurring revenue comes from instruments and accessories.


## 3. Is There Growing Demand For Its Products / Services?

```{r fig.width=7,echo=FALSE}
recurringRevenueGrowth <- 
  recurringRevenue %>% 
  filter(fiscal_year_ended >= ymd(20170101)) %>%
  select(fiscal_year_ended, segment, yoy_growth, met_growth_KPI)

ylim_max <- max(recurringRevenueGrowth$yoy_growth) * 1.05
hline_label <- '10% growth 
requirement'

ggplot(data = recurringRevenueGrowth
       , aes(x = format(fiscal_year_ended, '%Y'), y = yoy_growth)) +
  geom_col(aes(fill = met_growth_KPI), show.legend = FALSE) +
  facet_wrap(vars(segment)) +
  labs(x = 'Fiscal year', y = 'Year-over-year growth', colour = NULL) +
  ggtitle('Year-over-year growth for each recurring revenue segment') +
  geom_text(aes(label = paste(round(yoy_growth * 100, 1), '%', sep = ''))
            , vjust = -0.6, size = 3.3) +
  coord_cartesian(ylim = c(0, ylim_max)) +
  theme(plot.title = element_text(hjust = 0.5)
        , panel.grid = element_blank()
        , axis.text.y = element_blank()
        , axis.ticks.y = element_blank()) +
  geom_hline(aes(color = hline_label
                 , yintercept = growth_kpi)) +
  scale_color_manual(values = c('black')) +
  scale_fill_manual(values = c('Yes' = '#99ccff', 'No' = 'red'))
  
```

From this bar plot, it shows that there is growing demand for the company's products / services. "Instruments and accessories" and "operating lease" segments have accelerating growth in the demand.


## 3. Can The Company Operate Without Relying On External Funding?

```{r fig.width=5, echo=FALSE}
fcfMgn <- 
    head(financial, n = 3) %>%
    select(fiscal_year_ended, fcf_margin)

ylim_max <- max(fcfMgn$fcf_margin) * 1.04

ggplot(data = fcfMgn
       , aes(x = format(fiscal_year_ended, '%Y-%b'), y = fcf_margin)) +
    geom_col(fill = '#99ccff') +
    labs(x = 'Fiscal year ended', y = 'Free cash flow margin') +
    ggtitle('Free cash flow margin (2017 to 2019)') +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)
          , panel.grid = element_blank()
          , axis.text.y = element_blank()) +
    geom_text(aes(label = paste(round(fcf_margin * 100, 1), '%', sep = ''))
                  , vjust = -0.6, size = 3.3) +
    coord_cartesian(ylim = c(0, ylim_max))
```

This bar plot shows that it is able to get cash profit from at least 26.2% of its revenue for the past 3 fiscal years. It also does not have any debt. This shows that it is able to operate without relying on external funding.


## Conclusion

From the analysis, it shows that:

* The company has recurring revenue which is about 72% of total revenue.
* There is growing demand for the company's products / services.
* It is able to operate without relying on external funding.

One risk that I noted is that negative publicity, whether accurate or inaccurate, concerning the da Vinci Surgical System could reduce market acceptance of the da Vinci Surgical System and could result in decreased product demand and decline in revenue.

Because of this risk, I limit my allocation to this stock to 2% of my portfolio value.
