---
title: "Stock Analysis Of Intuitive Surgical, Inc"
author: "Steffen Zou Weilun"
date: "10 November 2020"
output:
  pdf_document: default
  html_document: default
---

Intuitive Surgical, Inc is known for its da Vinci Surgical Systems. The da Vinci Surgical System is a platform for robotic-assisted surgery, designed to enable complex surgery using a minimally invasive approach. 

I will explore the company's financial data to find out the following:

1. Is there demand for its products / services?
2. Does it have recurring revenue?
3. Can the company operate without relying on external funding?

```{r message=FALSE, echo=FALSE}
library(readxl)
library(dplyr)

financial <- read_excel('ISRG.xlsx', sheet = 'overall')
recurringRevenue <- read_excel('ISRG.xlsx', sheet = 'recurring revenue')

names(financial) <- gsub('[ -]', '_', names(financial))
names(recurringRevenue) <- gsub(' ', '_', names(recurringRevenue))

# Calculate year-over-year gross profit growth
yoy_gross_profit_growth <- with(financial
                                , gross_profit[-nrow(financial)] / 
                                             gross_profit[-1] - 1)
yoy_gross_profit_growth <- c(yoy_gross_profit_growth, NA)
financial$yoy_gross_profit_growth <- yoy_gross_profit_growth

# Calculate recurring revenue as proportion of total revenue
financial$proportion_recurring <- with(financial
                                       , recurring_revenue / total_revenue)

# Calculate free cash flow and free cash flow margin
financial <- 
    mutate(financial
           , free_cash_flow = operating_cash_flow - capital_expenditure
           , fcf_margin = free_cash_flow / total_revenue)
```


## 1. Is There Demand For Its Products / Services?

```{r fig.width=5, echo=FALSE}
library(ggplot2)

demand <- 
    head(financial, n = 3) %>%
    select(fiscal_year_ended, yoy_gross_profit_growth)

ylim_max <- max(demand$yoy_gross_profit_growth) * 1.04

ggplot(data = demand
       , aes(x = format(fiscal_year_ended, '%Y-%b')
             , y = yoy_gross_profit_growth)) +
    geom_col(fill = '#99ccff') +
    labs(x = 'Fiscal year ended', y = 'Year-over-year gross profit growth') +
    ggtitle('Year-over-year gross profit growth (2017 to 2019)') +
    theme_minimal() +
    geom_text(aes(label = paste(round(yoy_gross_profit_growth * 100, 1)
                                , '%', sep = ''))
              , vjust = -0.6, size = 3.3) +
    coord_cartesian(ylim = c(0, ylim_max)) +
    theme(panel.grid = element_blank()
          , plot.title = element_text(hjust = 0.5)
          , axis.text.y = element_blank())
```

From this bar plot, it shows that the year-over-year gross profit growth is at least 16.3% for the past 3 fiscal years, and that the growth is accelerating. This shows that there is demand for the company's products / services.


## 2. Does It Have Recurring Revenue?

```{r fig.width=5, echo=FALSE}
recurring <-
    head(financial, n = 3) %>%
    select(fiscal_year_ended, proportion_recurring)

ylim_max <- max(recurring$proportion_recurring) * 1.04
title <- 'Recurring revenue as proportion of total revenue 
(2017 to 2019)'
    
ggplot(data = recurring
       , aes(x = format(fiscal_year_ended, '%Y-%b')
             , y = proportion_recurring)) +
    geom_col(fill = '#99ccff') +
    labs(x = 'Fiscal year ended', y = 'Proportion of total revenue') +
    ggtitle(title) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)
          , panel.grid = element_blank()
          , axis.text.y = element_blank()) +
    coord_cartesian(ylim = c(0, ylim_max)) +
    geom_text(aes(label = paste(round(proportion_recurring * 100, 1)
                                , '%', sep = ''))
              , vjust = -0.7, size = 3.1)
```

From this bar plot, it shows that the company has recurring revenue which is about 72% of total revenue.

```{r echo=FALSE}
fy_ended <- with(recurringRevenue
                 , as.Date(c(min(fiscal_year_ended)
                             , max(fiscal_year_ended))) )

recurringRevenue$segment <- 
    factor(recurringRevenue$segment
           , levels = c('Instruments and accessories', 'Services'
                        , 'Operating lease'))

ggplot(data = recurringRevenue
       , aes(x = as.Date(fiscal_year_ended), y = recurring_revenue
             , color = segment)) +
    geom_line(size = 1) +
    geom_point() +
    theme_light() +
    scale_x_date(breaks = fy_ended
                 , labels = function(x) {format(x, '%Y-%b')}) +
    scale_y_continuous(labels = function(x) {
        paste('$', format(x, big.mark = ','), 'M', sep = '')
        }) +
    labs(x = 'Fiscal year ended', y = 'Recurring revenue') +
    ggtitle('Recurring revenue segments (2015 to 2019)') +
    theme(plot.title = element_text(hjust = 0.5)
          , panel.grid = element_blank())
```

Its recurring revenue comes from instruments and accessories, services, and operating lease. Majority of its recurring revenue comes from instruments and accessories.


## 3. Can The Company Operate Without Relying On External Funding?

```{r fig.width=5, echo=FALSE}
fcfMgn <- 
    head(financial, n = 3) %>%
    select(fiscal_year_ended, fcf_margin)

ylim_max <- max(fcfMgn$fcf_margin) * 1.04

ggplot(data = fcfMgn
       , aes(x = format(fiscal_year_ended, '%Y-%b'), y = fcf_margin)) +
    geom_col(fill = '#99ccff') +
    labs(x = 'Fiscal year ended', y = 'Free cash flow margin') +
    ggtitle('Free cash flow margin (2017 to 2019)') +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)
          , panel.grid = element_blank()
          , axis.text.y = element_blank()) +
    geom_text(aes(label = paste(round(fcf_margin * 100, 1), '%', sep = ''))
                  , vjust = -0.6, size = 3.3) +
    coord_cartesian(ylim = c(0, ylim_max))
```

This bar plot shows that it is able to get cash profit from at least 26.2% of its revenue for the past 3 fiscal years. It also does not have any debt. This shows that it is able to operate without relying on external funding.


## Conclusion

From the analysis, it shows that:

* There is demand for the company's products / services.
* The company has recurring revenue which is about 72% of total revenue.
* It is able to operate without relying on external funding.

One risk that I noted is that negative publicity, whether accurate or inaccurate, concerning the da Vinci Surgical System could reduce market acceptance of the da Vinci Surgical System and could result in decreased product demand and decline in revenue.

Because of this risk, I limit my allocation to this stock to 2% of my portfolio value.
